---
title: "FST and Alpha Value Mapping Based on Base Pair Position"
author: "Brian Ferolito"
output: html_notebook
---

The following reads a text file with 4 columns. The first column is the index numbers of the 7,265 loci (beginning at 0
and ending at 7,264). The second column is the corresponding base pair position. The third and fouth columns are the FST 
and Alpha values, respectively. The columns are labeled and are stored into vectors.

```{r Read the file into a data frame}

fst_vs_pos<-read.table("~/Desktop/Lotterhos_Lab/fst_vs_pos.txt", col.names = c("Index", "Position", "FST", "Alpha", "Logarithm Posterior Odds", "Posterior Probability"))
fst_vs_pos
Base_Pair_Position<-fst_vs_pos[,2]
FST_Value<-fst_vs_pos[,3]
Alpha_Values<-fst_vs_pos[,4]
logOdds<-fst_vs_pos[,5]
Post.Prob<-fst_vs_pos[,6]
```

The following code plots the FST value by base pair position with a 95% quantile line. The two following quantile 
lines are constructed by obtaining the quantile value and plotting that value as the y intercept with a slope of 0.

```{r FST vs Base Pair Position}

library(tidyverse)

ggplot(data = fst_vs_pos) +
  geom_point(mapping = aes(x = Base_Pair_Position, y = FST_Value)) +
  geom_abline(mapping = aes(intercept = 0.012832 , slope = 0)) +
  ggtitle("10944")

  quantile(FST_Value, probs = (0.95))
  
```

The folloing code plots the Alpha value by base pair position with a 95% quantile line.

```{r Alpha Value vs Base Pair Position}

library(tidyverse)

ggplot(data = fst_vs_pos, mapping = aes(x = Base_Pair_Position, y = Alpha_Values)) +
  geom_point() +
  geom_abline(mapping = aes(intercept = 0.87006, slope = 0)) +
  ggtitle("10944")

  quantile(Alpha_Values, probs = (0.95))

```

```{r Log Post Odds}

library(tidyverse)
fst_vs_pos.filtered<-fst_vs_pos %>%
  filter(fst_vs_pos$Logarithm.Posterior.Odds != 1000)




ggplot(data = fst_vs_pos.filtered, mapping = aes(x = fst_vs_pos.filtered$Position, y = fst_vs_pos.filtered$Logarithm.Posterior.Odds)) +
  geom_point() +
  geom_abline(mapping = aes(intercept = 0.176422  , slope = 0)) +
  ylab("Logarithm of Posterior Odds") +
  xlab("Base Pair Position") +
  ggtitle("10944")

  quantile(fst_vs_pos.filtered$Logarithm.Posterior.Odds, probs = (0.95))

```


```{r}
library(tidyverse)

negativeLog.Post.Prob<-(-log(Post.Prob, 10))
ggplot(data = fst_vs_pos, mapping = aes(x = Base_Pair_Position, y = negativeLog.Post.Prob)) +
  geom_point() +
  geom_abline(mapping = aes(intercept = 1.171256, slope = 0)) +
  xlab("Base Pair Position") +
  ylab("-log10 Posterior Probability") +
  ggtitle("10944")

  quantile(negativeLog.Post.Prob, probs = (0.95))

```

